Penalized regression for left-truncated and right-censored survival data

### 2021-04-29 manuscript.tex
Minor wording edit
tweak Efron statement

where $\beta$ is the vector of regression coefficients and is maximized over \autoref{eqn:simon} subject to a constraint defined by $\lambda \cdot P_{\alpha}\beta$, and $P_{\alpha}\beta$ is the $l_1$ (lasso), $l_2$ (ridge), or elastic net penalty on the sum of coefficients $\beta$ described elsewhere \cite{simon2011regularization, tibshirani1996regression, tikhonov1963ridge, zou2005regularization}. The algorithm by Simon \emph{et al.} fits over a path of $\lambda$ values via cyclical coordinate descent. Instead of solving a least squares problem at each iteration, the algorithm solves a penalized reweighted least squares problem, in which observation weights $w$ are defined in the coordinate descent least squares minimization step. The optimal $\lambda$ can be identified through cross-validation. Tied survival times are handled via the Breslow approximation \cite{breslow1972} and details provided in \cite{simon2011regularization}. Note that the computationally efficient Efron approximation will be added to the next version of \pkg{glmnet}.

>>>>

where $\beta$ is the vector of regression coefficients and is maximized over \autoref{eqn:simon} subject to a constraint defined by $\lambda \cdot P_{\alpha}\beta$, and $P_{\alpha}\beta$ is the $l_1$ (lasso), $l_2$ (ridge), or elastic net penalty on the sum of coefficients $\beta$ described elsewhere \cite{simon2011regularization, tibshirani1996regression, tikhonov1963ridge, zou2005regularization}. The algorithm by Simon \emph{et al.} fits over a path of $\lambda$ values via cyclical coordinate descent. Instead of solving a least squares problem at each iteration, the algorithm solves a penalized reweighted least squares problem, in which observation weights $w$ are defined in the coordinate descent least squares minimization step. The parameter $\lambda$ can be identified through cross-validation. Tied survival times are handled via the Breslow approximation \cite{breslow1972} and details provided in \cite{simon2011regularization}. Note that the Efron approximation will be added to the next version of \pkg{glmnet}.
